[Re] A Generalized Linear Integrate-and-Fire Neural Model Produces Diverse Spiking Behaviors

### 2017-08-16 article/detorakis-2017.tex
more corrections

The model consists of linear differential equations, which describe the membrane
and threshold potentials and internal currents. All the results provided in 
\cite{mihalas:2009} have been obtained by using only two internal currents and
thus we use the exact same number of internal currents in this work. The
subthreshold dynamics are defined by a set of linear ordinary differential 
equations, while an instantaneous threshold potential controls when the neuron
firing an action potential (spike) in a dynamic way. The ability of the MNN 
model to generate 
such a diverse spiking behavior is due to the complex update rules. In this 
work the MNN model has been implemented in Python (version 3.6.1) using 
Numpy (version 1.13.1) and Matplotlib (version 2.0.2) packages.

@@

In order to implement the model described in \cite{mihalas:2009}, we discretized
the dynamical system using the forward Euler's integration scheme. The time step
is fixed to $0.1\, \Rm{ms}$ for all the simulations, and the total simulation
time $t_f$ varies according to figure 1 of the original paper. Our
implementation differs from the one in the original paper, since in
\cite{mihalas:2009}, authors numerically solve equation $3.5$ (algebraic 
equation) under the constraint imposed by inequality $3.4$ and thus they
compute the spike times. On the other hand, in this work we directly compute
numerically the solution of the dynamical system defined by equations $2.1$
and $2.2$ in \cite{mihalas:2009} (see tables~\ref{table:2} and~\ref{table:3}).

@@

All three figures from the original article have been successfully replicated.
All the different spiking behaviors of the model are illustrated in 
Figure~\ref{fig:1}, where the black solid line indicates the membrane potential
($V(t)$), the red dashed line illustrates the instantaneous threshold potentials
($\Theta(t)$), and the gray line shows the input to the neuron ($I_e/C$). 
The $x$-axis scale in all the panels are exactly the same as in the original
paper (indicating the total simulation time ($t_f$), while the $y$-axis scale 
differs from the one in the original paper. In this work the $y$-axis scale
is the same same for all the subplots ($[-95, -25]\, \Rm{mV}$), except from
panels G and O ($[-145, -25]\, \Rm{mV}$).

>>>>

The model consists of linear differential equations, which describe the membrane
and threshold potentials and internal currents. All the results provided in 
\cite{mihalas:2009} have been obtained by using only two internal currents and
thus we use the exact same number of internal currents in this work. The
subthreshold dynamics are defined by a set of linear ordinary differential 
equations, while an instantaneous threshold potential controls when the neuron
fires an action potential (spike) in a dynamic way. The ability of the MNN 
model to generate 
such a diverse spiking behavior is due to the complex update rules. In this 
work the MNN model has been implemented in Python (version 3.6.1) using 
Numpy (version 1.13.1) and Matplotlib (version 2.0.2) packages.

@@

In order to implement the model described in \cite{mihalas:2009}, we discretized
the dynamical system using the forward Euler integration scheme. The time step
is fixed to $0.1\, \Rm{ms}$ for all the simulations, and the total simulation
time $t_f$ varies according to figure 1 of the original paper. Our
implementation differs from the one in the original paper, since in
\cite{mihalas:2009}, authors numerically solve equation $3.5$ (algebraic 
equation) under the constraint imposed by inequality $3.4$ and thus they
compute the spike times. On the other hand, in this work we directly compute
numerically the solution of the dynamical system defined by equations $2.1$
and $2.2$ in \cite{mihalas:2009} (see tables~\ref{table:2} and~\ref{table:3}).

@@

All three figures from the original article have been successfully replicated.
All the different spiking behaviors of the model are illustrated in 
Figure~\ref{fig:1}, where the black solid line indicates the membrane potential
($V(t)$), the red dashed line illustrates the instantaneous threshold potentials
($\Theta(t)$), and the gray line shows the input to the neuron ($I_e/C$). 
The $x$-axis scales in all panels are exactly the same as in the original
paper (indicating the total simulation time ($t_f$), while the $y$-axis scale 
differs from the one in the original paper. In this work the $y$-axis scale
is the same same for all the subplots ($[-95, -25]\, \Rm{mV}$), except for
panels G and O ($[-145, -25]\, \Rm{mV}$).
